% !TEX TS-program = lualatex
%-------------------------
% Rezume, a latex resume template for developers
% Author : Nanu Panchamurthy
% Based off of: https://github.com/sb2nov/resume
% License : MIT

% Hope this resume template helps you land an awesome job. If you found this helpful, please consider starring the github repo here, .
%-------------------------



%------------PACKAGES----------------
\documentclass[a4paper,11pt]{article}

\usepackage{verbatim} % reimplements the "verbatim" and "verbatim*" environments

\usepackage{titlesec} % provides an interface to sectioning commands i.e. custom elements
\usepackage{fontspec}

\usepackage{wasysym}

\usepackage{color} % provides both foreground and background color management
\usepackage{xcolor}

\usepackage{enumitem} % provides control over enumerate, itemize and description

\usepackage{fancyhdr} % provides extensive facilities for constructing headers, footers and also controlling their use

\usepackage{tabularx} % defines an environment tabularx, extension of "tabular" with an extra designator x, paragraph like column whose width automatically expands to fill the width of the environment

\usepackage{latexsym} % provides mathematical symbols



\usepackage{marvosym} % provides martin vogel's symbol font which contains various symbols

\usepackage[empty]{fullpage} % sets margins to one inch and removes headers, footers etc..

\usepackage[hidelinks]{hyperref} % removes color and shadow of hyperlinks

\usepackage[normalem]{ulem} % provides "\ul" (uline) command which will break at line breaks

\usepackage[english]{babel} % provides culturally determined typographical rules for wide range of languages
%-----------------------------------------

%----------FONT OPTIONS-------------------
\usepackage[default]{sourcesanspro} % uses the font source sans pro
\urlstyle{same} % changes url font from default urlfont to font being used by the document

\newfontfamily{\headingfont}{AvenirLTProBook.otf}[
    % Optional: Add font features like bold, italic, etc.
    % BoldFont = YourOTFFontName-Bold.otf,
    % ItalicFont = YourOTFFontName-Italic.otf,
]


%-----------------------------------------



%----------MARGIN OPTIONS-----------------
\pagestyle{fancy} % set page style to one configured by fancyhdr
\fancyhf{} % clear all header and footer fields

\renewcommand{\headrulewidth}{0in} % sets thickness of linerule under header to zero
\renewcommand{\footrulewidth}{0in} % sets thickness of linerule over footer to zero
\setlength{\parskip}{1em}

% origin of the document is one inch from the top and from and the left
% oddsidemargin and evensidemargin both refer to the left margin
% right margin is indirectly set using oddsidemargin
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\topmargin}{-0.5in}

\addtolength{\textwidth}{1.0in} % sets width of text area in the page to one inch
\addtolength{\textheight}{1.0in} % sets height of text area in the page to one inch

\raggedbottom{} % makes all pages the height of current page, no extra vertical space added
\raggedright{} % makes all pages the width of current page, no extra horizontal space added
%------------------------------------------


%--------SECTIONING COMMANDS---------
% \titleformat{<command>}
%   [<shape>]{<format>}{<label>}{<sep>}
%     {<before-code>}[<after-code>]

% command is the sectioning command to be redefined
% shape is the style of the font; scshape stands for small caps style
% format is the format to be applied to whole title- label and text; absent here
% label defines the label
% sep is the horizontal separation between label and title body
% before-code is the code to be executed before
% after-code is the code to be executed after

\titleformat{\section}
{\large\bfseries}{}
{0em}{\textcolor[HTML]{e5ff80}}[\color{black}\titlerule\vspace{0pt}]
%-------------------------------------



%__________________RESUME____________________
% You can rearrange sections in any order you may prefer
\begin{document}
	
	
	\hypersetup{
		pdftitle={A well written resume},
		pdfauthor={Babak Firoozi Fooladi},
		pdfsubject={A brief description of my talents and skills.},
		pdfkeywords={self-driven, motivated, data analyst, data scientist, domain expert, economics, data visualisation, graphic design, Perfect RAG designer, Agentic AI, LLMs}
	}

	\section{Cover Letter}


	Dear Hiring Team at Recordly,

I am writing to express my strong interest in the Junior Data Engineer position at Recordly. I am currently a Ph.D. candidate at Aalto University, where I have gained extensive hands-on experience in data engineering; however, I recognise that I lack experience in production environments and business-orientated practices. This position represents a solid opportunity for me to solidify my foundation in the field of data engineering. I am keen on learning and have honed my skills in acquiring knowledge, critical thinking, radical creativity, and a growth-oriented mindset.

As detailed in my CV, my background includes deploying Azure functions for automated data collection, designing ETL/ELT pipelines from various sources, including REST APIs, and building data infrastructure using PostgreSQL and DuckDB. I was responsible for the research data infrastructure within my team, focusing on acquiring, processing, and storing data from real estate transactions. These experiences have equipped me to work as an independent analytics engineer for Apex-Heat, where I successfully tackled challenges with their code stack, resulting in a recommendation letter that I have attached to my application. My self-taught programming journey, later formalised through formal data science education, reflects the enthusiasm for learning and adaptability that you seek in candidates.

I am particularly attracted to Recordly's vision of defining the interaction between humans and data. These goals align perfectly with my interest in addressing the diverse challenges and problems across various domains. I am adept at transferring my knowledge and skills across different fields to produce creative and innovative solutions. While I am currently learning Finnish, I am fluent in English and am a native Farsi speaker, which also enables me to engage with texts in Arabic, Persian, Urdu, and Kurdish, making me a valuable asset.

I see this job opportunity to further transform my skills and knowledge into actionable solutions for business practices. I would welcome the opportunity to discuss how my practical experience with modern data solutions and my commitment to continuously expanding my technical skills can contribute to Recordly's growth and assist your customers in achieving their data transformation goals.

Sincerely yours,
Babäk Firoozi Fooladi

\end{document}