% !TEX TS-program = lualatex
%-------------------------
% Rezume, a latex resume template for developers
% Author : Nanu Panchamurthy
% Based off of: https://github.com/sb2nov/resume
% License : MIT

% Hope this resume template helps you land an awesome job. If you found this helpful, please consider starring the github repo here, .
%-------------------------



%------------PACKAGES----------------
\documentclass[a4paper,11pt]{article}

\usepackage{verbatim} % reimplements the "verbatim" and "verbatim*" environments

\usepackage{titlesec} % provides an interface to sectioning commands i.e. custom elements
\usepackage{fontspec}

\usepackage{wasysym}

\usepackage{color} % provides both foreground and background color management
\usepackage{xcolor}

\usepackage{enumitem} % provides control over enumerate, itemize and description

\usepackage{fancyhdr} % provides extensive facilities for constructing headers, footers and also controlling their use

\usepackage{tabularx} % defines an environment tabularx, extension of "tabular" with an extra designator x, paragraph like column whose width automatically expands to fill the width of the environment

\usepackage{latexsym} % provides mathematical symbols



\usepackage{marvosym} % provides martin vogel's symbol font which contains various symbols

\usepackage[empty]{fullpage} % sets margins to one inch and removes headers, footers etc..

\usepackage[hidelinks]{hyperref} % removes color and shadow of hyperlinks

\usepackage[normalem]{ulem} % provides "\ul" (uline) command which will break at line breaks

\usepackage[english]{babel} % provides culturally determined typographical rules for wide range of languages
%-----------------------------------------

%----------FONT OPTIONS-------------------
\usepackage[default]{sourcesanspro} % uses the font source sans pro
\urlstyle{same} % changes url font from default urlfont to font being used by the document

\newfontfamily{\headingfont}{AvenirLTProBook.otf}[
    % Optional: Add font features like bold, italic, etc.
    % BoldFont = YourOTFFontName-Bold.otf,
    % ItalicFont = YourOTFFontName-Italic.otf,
]


%-----------------------------------------



%----------MARGIN OPTIONS-----------------
\pagestyle{fancy} % set page style to one configured by fancyhdr
\fancyhf{} % clear all header and footer fields

\renewcommand{\headrulewidth}{0in} % sets thickness of linerule under header to zero
\renewcommand{\footrulewidth}{0in} % sets thickness of linerule over footer to zero
\setlength{\parskip}{1em}

% origin of the document is one inch from the top and from and the left
% oddsidemargin and evensidemargin both refer to the left margin
% right margin is indirectly set using oddsidemargin
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\topmargin}{-0.5in}

\addtolength{\textwidth}{1.0in} % sets width of text area in the page to one inch
\addtolength{\textheight}{1.0in} % sets height of text area in the page to one inch

\raggedbottom{} % makes all pages the height of current page, no extra vertical space added
\raggedright{} % makes all pages the width of current page, no extra horizontal space added
%------------------------------------------


%--------SECTIONING COMMANDS---------
% \titleformat{<command>}
%   [<shape>]{<format>}{<label>}{<sep>}
%     {<before-code>}[<after-code>]

% command is the sectioning command to be redefined
% shape is the style of the font; scshape stands for small caps style
% format is the format to be applied to whole title- label and text; absent here
% label defines the label
% sep is the horizontal separation between label and title body
% before-code is the code to be executed before
% after-code is the code to be executed after

\titleformat{\section}
{\large\bfseries}{}
{0em}{\textcolor[HTML]{0f7a5a}}[\color{black}\titlerule\vspace{0pt}]
%-------------------------------------



%__________________RESUME____________________
% You can rearrange sections in any order you may prefer
\begin{document}
	
	
	\hypersetup{
		pdftitle={A well written resume},
		pdfauthor={Babak Firoozi Fooladi},
		pdfsubject={A brief description of my talents and skills.},
		pdfkeywords={self-driven, motivated, data analyst, data scientist, domain expert, economics, data visualisation, graphic design, Perfect RAG designer, Agentic AI, LLMs}
	}

	\section{About the job}

Source: https://www.linkedin.com/jobs/search/?currentJobId=4310808788

About the job
The application period for OP Financial Group's 2026 Kiitorata Trainee Program is now open! We are looking for approximately 40 open-minded and courageous talents for diverse, challenging, and skill-enhancing roles in various business areas.

Are you interested in technology research and eager to shape the future of OP? OP Lab needs top talent to steer our journey through the financial sector's technological transformation and rapidly turn promising technologies and ideas into experiments and prototypes. The findings are distilled into clear reports that support the adoption of an emerging technology.

We are now seeking a Technology Exploration Trainee for OP Financial Group's innovation unit, OP Lab!

As a Technology Exploration trainee, your role is to support technology research and experimentation activities at OP Lab. You will scan emerging tech, frame hypotheses, build and test lightweight prototypes, evaluate outcomes with user feedback and metrics, and distill clear, decision-ready reports. You'll bring systems thinking and fresh ideas to improve our experimentation process, share learnings to strengthen our culture, and tailor your scope - from research and analysis to designing and running experiments - based on your skills and interests. By the end of the traineeship, you'll have hands-on experience in rapid prototyping, experiment design, and impact measurement, and a broad understanding of moving new technology toward adoption.

Does this sound like you?

You are a curious, outward-looking problem-solver who wants to broaden your technological expertise and hypothesis-driven thinking. You see the big picture, apply new technology to create business value, and measure the impact. You enjoy collaborating with others and approach new technologies and ideas with an open mind. You constructively challenge established ways of working and introduce new methods that strengthen OP Lab's ability to accelerate innovation.

Your working style is systematic, yet you can operate creatively amid uncertainty and unfinished work. You communicate fluently in English and distill results into clear demos, presentations, or reports. We also appreciate the ability to communicate in Finnish. You design and run lightweight experiments and objectively assess their usefulness based on feedback and metrics. You are in the final stages of your university studies or a recent graduate, and your background may be diverse in terms of education, work experience, and international exposure. Most important is a genuine interest in technology and a desire to apply what you've learned in practice.

A Few Words About Us…

You will become part of the talented team of OP Lab, where you'll help inspire innovation across OP Financial Group. Here, you'll enjoy a variety of engaging tasks and shape not only your work but also your career within our close-knit group of 30 colleagues. Whether you join us in Vallila, Helsinki or in our new campus in Oulu, we look forward to seeing you in person two to three anchor days a week, and for the rest of the time, you're free to choose between working remotely or onsite.

…and why you should work for us

OP Lab's role involves identifying future phenomena, analyzing them, integrating them into the business context, and testing the feasibility and attractiveness of business opportunities. We accelerate innovation by implementing special projects that achieve significant business improvements through the application of new business models, technologies, or ways of working. If you're eager to learn, grow, and make a real impact, OP Lab is the place to start your journey.

At OP, you will work on challenging tasks of daily life, and in addition to gaining a vast amount of life skills and new expertise, you will be a part of Finland's most attractive financial industry player. With your actions and a determined attitude, you can influence your own career path here. We support your personal development and encourage you boldly! You will be employed by OP for a paid six-month contract from March 1 to August 31, 2026, and we offer the same salary to you and all trainee colleagues; €3,150 per month.

To help counterbalance work where you are expected to take a lot of responsibility, we seek to ensure employee wellbeing and to enable forward-looking work arrangements. We offer a stable working environment where you can contribute to our core values responsibility, people first and succeeding together.

You will enjoy a wide range of staff benefits, including a personnel fund and special terms for employee banking, insurance and loan services. We offer comprehensive occupational health care, extensive medical treatment expenses insurance and a full-time group accident insurance policy. We invest in wellbeing at work by encouraging a good work-life balance, providing flexibility in your daily life, and offering lunch, sport and cultural benefits and opportunities for affordable holidays in OP timeshares.

Join our team of future stars!

If you have any questions about the position or working with us, you can get more information from Technology Exploration Lead Petri Liimatta p. +358 400777035. You can reach Petri on Fri Oct 10 from 12 PM to 1 PM or Tue Oct 10 from 12 PM to 1 PM.

Next, we would like to hear more about you, so apply by telling us about your skills and motivation in the form of an application and video responses. Apply for the position by Sunday, October 19, 2025, at the latest by 1) submitting your application documents via the Apply Now button and 2) additionally responding to our video interview questions through this link.

We will start processing applications as soon as the application period opens, so explore our diverse trainee positions and send your application to us today!

Here's How Our Application Process Works

Apply for the positions by October 19, 2025, through OP's career site where you can find job-specific job postings and additional information about the Kiitorata Trainee Program. Please submit your application documents via the Apply Now button and additionally respond to our video interview questions through this link. Please note that progressing to the next stage requires both submitting your application documents through our application portal and providing video responses to our questions.

We will contact all applicants regarding further steps by Tuesday, November 11, 2025. Those selected for personal interviews will be contacted by phone to arrange an interview date, and those not selected will be informed via email.

We will interview and announce selection decisions to the finalist candidates by December 19, 2025. As part of the selection process, all finalist candidates will undergo personality assessments.

The employment contract will be for the period from March 1 to August 31, 2026.

We operate in the financial sector and our business is founded on trust and accountability. For this reason, we will check the successful candidate's credit history, corporate connections and potential conflicts of interest. In addition, the successful candidate must take a drug test.

OP Financial Group – We have something in common

Diversity and equality are highly prized at OP Financial Group. We want everyone to feel welcome and valued, and we appreciate that diversity enriches us and brings new perspectives. We invite job applications from everyone, because we all have something in common. We're thrilled that you want to join us on our shared journey.

Owned by our customers, we are the most attractive financial sector employer in Finland. Our Group employs more than 14,000 professionals. We have a mission – to promote the sustainable prosperity, security and wellbeing of our owner-customers and operating region. What we do matters, both to our employees and society in general. As the largest financial services group in Finland, we are building a better tomorrow; this has been our goal for more than 120 years.

Kiitorata2026
\end{document}